A few closing notes, restrictions, hints, and tips that didn't fit 
elsewhere in the manual\ldots

\begin{itemize}
\item{Any SERPENT2 material with either a conditions block or one or more
streams, must have the keyword \texttt{ader} appear in the material's definition
before the listing of the material's constituent isotopes.}
\item{If the user would like ADER to issue a warning every time the burnup
solution produces a negative density for an isotope, which is then corrected to
zero, place the following line in the simulation input. The value is arbitrary.
\begin{lt}
set ader_neg_adens [value]
\end{lt}
    }
\item{ADER is not compatible with divided SERPENT2 materials. These may be used
in the same simulation but divided materials, or their children, may not also
be materials under ADER control.}
\item{ADER is not compatible with SERPENT2's ``\texttt{mflow}" structure.
Materials affected by \texttt{mflow} structures may be used in an ADER
simulation but they may not in any way (other than neutronically) be connected
with ADER or ADER materials.}
\item{SERPENT2 employs a function, \texttt{MaterialBurnup}, which calculates
the power produced by a material during a burnup step by the difference
in abundances of isotopes in that material between the beginning of the burnup
step and the end of the burnup step. This methodology assumes there are no
mass flows in the system and has not been configured to incorporate ADER mass
flows. AS SUCH - MATERIAL POWER ESTIMATES PROVIDED BY SERPENT2 WHEN RUNNING
AN ADER SIMULATION WITH AT LEAST ONE CONTINUOUS OR PROPORTIONAL STREAM ARE
LIKELY INCORRECT. The user can fix these power estimates themselves by 
incorporating the mass moved by streams and the power produced from any 
fissions on these masses.}
\item{ADER's oxidation table structure does not recognize elements higher
than Rg on the periodic table.}
\item{On EVERY Monte-Carlo sweep SERPENT prints out cycle-wise data into the
\texttt{[name]\_res.m} file. Every ADER iteration will produce a new entry for
the same burnup step in this file with older entries becoming invalid but
not erased. Be aware.}
\end{itemize}
