\documentclass{article}

\usepackage[right=1in,left=1in,top=1in,bottom=1in]{geometry}

\usepackage{mhchem}

\usepackage{xcolor}

\usepackage{blkarray}

\usepackage{amsmath}

\usepackage{amsfonts}

\usepackage{tikz}
\usetikzlibrary{shapes.geometric, arrows}
\usetikzlibrary{arrows, decorations.markings}
\usetikzlibrary{positioning}

\tikzstyle{startstop} = [rectangle, rounded corners, minimum width=3cm, minimum height=1.0cm, text centered, draw=black, fill=lightgray]
\tikzstyle{process} = [rectangle, minimum width=6cm, minimum height=1.0cm, text width = 5cm, text centered, draw=black, fill=lightgray]
\tikzstyle{decision} = [diamond, minimum width=2cm, minimum height=1cm, text width = 3cm, text centered, draw=black, fill=lightgray]
\tikzstyle{io} = [trapezium, trapezium left angle=70, trapezium right angle=110, minimum width=3cm, text width = 3cm, minimum height=1cm, text centered, draw=black, fill=lightgray]
\tikzstyle{arrow} = [thick,->,>=stealth]

\usepackage{amsmath}

\numberwithin{equation}{section}

\usepackage{listings}

%Create the color for the code background
\definecolor{light-gray}{gray}{0.85}

% This makes a listing environment for input templates 

\lstnewenvironment{lt}
{
    \lstset{
        basicstyle=\ttfamily,
        backgroundcolor=\color{light-gray},
        emph={action, ader_neg_adens, ader_trans_iter, burn, cnd, cnt, cont, control, conditions, dir, disc, feed, feed_and_remv, form, frac, from, group, grp, grp2, isos, keyword, kmax, kmin, mass, mat, max, min, mols, omp, opt, oxi, oxidation, pres, prop, reac, redox, rem, remv, rhow, rng, rto, set, spec_stream, stream, streams, sum, to, transfers, type, val, vol, weight},
        emphstyle=\underbar,
    }
}{}

% This makes a listing environment for input examples
\lstnewenvironment{li}
{
    \lstset{
        basicstyle=\bfseries\color{white},
        backgroundcolor=\color{black},
    }
}{}

\begin{document}

\title{ADER: Advanced Depletion Extension for Reprocessing\\
\vspace{10pt}\large{Ver: 1.0 - A SERPENT2 Extension}\\
\vspace{10pt}\large{User Manual}}

\author{
    Daniel D. Wooten
}

\clearpage
\maketitle
\pagebreak
\tableofcontents
\pagebreak

\section{Preface}\label{sec:pref}
This document is intended for users of SERPENT2 wishing to utilize the
\textbf{A}dvanced \textbf{D}epletion \textbf{E}Extension for
\textbf{R}eprocessing ( ADER ) extension.
\textbf{This manual assumes the reader is proficient with SERPENT2.}
General information about SERPENT2 can be found at the SERPENT2
wiki: 
\begin{lstlisting}[breaklines, backgroundcolor=\color{white}]{website}
serpent.vtt.ft/mediawiki/index.php/Main_Page
\end{lstlisting}

With regards to citing SERPENT2 and ADER, as stated on the SERPENT2 wiki general
reference to SERPENT2 may be provided by - J. Leppanen, M. Pusa, T. Vittanen,
V. Valtavirta, T. Kaltiaisenaho. \textit{``The Serpent Monte Carlo code: Status,
development, and applications in 2013"}. Ann. Nucl. Energy, \textbf{82} (2015)
142 - 150. Reference to ADER may be provided by - D. D. Wooten. \textit{ADER -
Advanced Depletion Extension for Reprocessing}. (2019).

ADER makes extensive use of the open-source library, Clp, part of the COIN-OR
collection of packages. Supporting documentation and the source code
for Clp can be found at: 
\begin{lstlisting}[breaklines, backgroundcolor=\color{white}]{website}
https://github.com/coin-or/Clp
\end{lstlisting}
Of importance is that Clp is distributed under
the Eclipse Public Licence which is not a copy-left licence but a rather
forgiving open-source licence. Instructions for installing and linking the
Clp libraries can be found in section \ref{sec:install}.

\noindent Examples of SERPENT2 input are given 
\begin{lt}
in this font
\end{lt}
SERPENT2 and ADER keywords, user inputs which must be a certain word, 
appear underlined as seen below. \textbf{Keywords not enclosed in brackets
must appear in the position of the entry they are seen in. Keywords enclosed in
brackets may appear anywhere after this opening keyword but must be followed
by their input value if they have one.}
\begin{lt}
keyword
\end{lt}
The following list of symbols are not to be considered ``input". Rather, they
are delimiters for this manual and should not be considered part of any ADER
commands or inputs\ldots
\begin{lt}
[ ] { } < > ( ) ; ...
\end{lt}
Required user inputs are denoted\ldots
\begin{lt}
[This_entry_is_set_by_the_user]
\end{lt}
Optional user inputs are denoted\ldots 
\begin{lt}
<This_entry_may_be_excluded>
\end{lt}
Required user choices from a list are denoted\ldots
\begin{lt}
[{option_1; option_2}]
\end{lt}
Optional user choices from a list are denoted\ldots
\begin{lt} 
<{option_1; option_2}>
\end{lt}
User inputs which are required \textit{if} a previous input was given are 
denoted\ldots
\begin{lt}
<optional_input> (required_input_due_to_earlier_input)
\end{lt}
If an example of a user input includes a structure such as\ldots
\begin{lt}
[Entry_1] [some_number]
...
<Entry_n> (some_number)
\end{lt}
This indicates that at least one instance of \texttt{Entry x} must be input by
the user but as many instances of type \texttt{Entry x} may be input by the
user. Additionally the presence of the second bracketed input indicates that
each instance of \texttt{Entry x} requires an entry of \texttt{some\_number}.
Examples of generic SERPENT2 input, input templates, are given in a light-gray
box with black mono-spaced font such as the example seen below\ldots

\begin{lt}
mat [mat_name] [mat_den] <{vol,mass}> [mat_val] <burn> (burn_segments) 
[isotope_1_zai].[temp_lib] [iso_frac]
<isotope_n_zai>.(temp_lib) (iso_frac)
\end{lt}

While any specific use examples, implementations of SERPENT2 input, are given
in a black box with white mono-spaced font such as the example seen below\ldots

\begin{li}
mat water -1.0 vol 1.0 burn 0.0
1001.06c    2
...
1608.06c    1
\end{li}

\section{Introduction}\label{sec:intro}

\textit{Please be sure to read the preface for important information.}\\
In the most direct sense ADER seeks to accomplish two tasks: 
determining an  optimal  material  composition  given  a  set  
of  constraints,  and  integrating the necessary composition adjustments 
into a nuclear material evolution model.
ADER brings to Serpent 2 the ability to define groups of elements,
isotopes, and chemicals; the ability to define relationships between these 
groups; and the ability to move these groups into, out-of, and between 
materials. Furthermore, ADER provides the ability to set
$k_{eff}$ targets, to prescribe mass transfers within a given system, and to set
weighted oxidation state targets for materials. Bringing all of these
capabilities together ADER employs the COIN-OR linear optimization (CLP) 
package to determine the material flows, as  set by the user, 
that will best satisfy an optimization target, also set by the user. 
Sufficiently simplified - ADER is a material-composition, linear-optimization
engine for the SERPENT2 burnup routines. 

This manual serves as both a reference for the theory of ADER and as a guide to
its usage. As such each section has a ``Quick Reference" subsection where
direct and simplified answers to common usage questions and input formatting
can be found. However, many users will find that a deeper understanding of the
theory behind ADER, as well as the nuances of its use, will serve them well. 
This manual is organized to be red through in a linear fashion by a first time
user beginning with the concept of a ``group" as it is used in ADER and
building up the ADER toolkit from there.

To provide context for the explanation of the components of ADER components of
an example simulation are built up throughout this manual. These components only
serve as rough examples.
That said, for this example consider a fuel salt for
a liquid fuel molten salt reactor composed of \ce{LiF} salt at 71.7
mol-fraction, \ce{BeF2} salt at 16 mol-fraction,
\ce{UF3} at 0.023 mol-fraction, \ce{UF4} at 2.277 mol-fraction, 
and \ce{ThF4} at 10 mol-fraction. Take this salt to have
an initial neutron multiplication factor of $1.0$ ( it does not in reality )
and to be in an infinite lattice with a graphite moderator which takes up 50\%
of the volume. The SERPENT2 material based off this example is shown below.
\textbf{The keyword ``ader" must be included in the definition line of any 
material which is to be managed by the ADER extensions to SERPENT2 - i.e. the
material is either connected to a stream or to a conditions block.} ADER input
is entered as a ``regular" component of SERPENT2 input files.

\begin{li}
mat FuelSalt -2.805 vol 1 burn 0 ader
3006.06c    0.00028
3007.06c    0.28323
4009.06c    0.06328
9019.06c    0.60450
90232.06c   0.03954
92233.06c   0.00046
92238.06c   0.00864
\end{li}

\section{Groups}\label{sec:groups}
\input{groups}

\section{Conditions Blocks}\label{sec:conditions_blocks}
\input{conditions_blocks}

\section{Streams}\label{sec:streams}
\input{streams}

\section{Criticality Control}\label{sec:criticality_control}
\input{criticality_control}

\section{Output}\label{sec:output}
\input{output}

\section{Testing}\label{sec:test}
\input{test}

\section{Parallel Computation}\label{sec:parallel}
\input{parallel}

\section{General Notes}\label{sec:general_notes}
\input{general_notes}

\section{Theory}\label{sec:theory}
\input{theory}

\section{Installation}\label{sec:install}
\input{install.tex}

\end{document}
