\documentclass{article}

\begin{document}

\title{ADER: Advanced Depletion Extension for Reprocessing\\
\vspace{10pt}\large{Ver: 1.0 - A SERPENT2 Extension}\\
\vspace{10pt}\large{Application Interface}}

\author{
    Daniel D. Wooten
}

\clearpage
\maketitle
\pagebreak

\tableofcontents
\pagebreak

\section{Preface}\label{sec:pref}
This document is intended for developers of SERPENT2 and specifically those
developers who wish to modify the ADER portions of SERPENT2. For users of
General information about SERPENT2 can be found at the SERPENT2
wiki: \verb|serpent.vtt.ft/mediawiki/index.php/Main_Page|
While ADER specific help can be found in the ADER user manual.
\\
With regards to citing SERPENT2 and ADER, as stated on the SERPENT2 wiki general
reference to SERPENT2 may be provided by - J. Leppanen, M. Pusa, T. Vittanen,
V. Valtavirta, T. Kaltiaisenaho. \textit{``The Serpent Monte Carlo code: Status,
development, and applications in 2013"}. Ann. Nucl. Energy, \textbf{82} (2015)
142 - 150. Reference to ADER may be provided by - D. D. Wooten. \textit{ADER -
Advanced Depletion Extension for Reprocessing}. (2019).
\\
ADER makes extensive use of the open-source library, Clp, part of the COIN-OR
collection of packages. Supporting documentation for Clp can be found at: 
\verb|https://github.com/coin-or/Clp|
Of importance is that Clp is distributed under
the Eclipse Public Licence which is not a copy-left licence but a rather
forgiving open-source licence. Instructions for installing and linking the
Clp libraries can be found in the user's manual.

\section{Introduction}\label{sec:intro}
ADER is a source code extension to SERPENT2. Originally developed by Daniel 
Wooten at the University of California Berkeley ADER provides four key features
to users of SERPENT2 - the ability to define relationships between isotopes,
elements, and chemicals in a SERPENT2 material; the ability to define how
the composition of these SERPENT2 materials may be adjusted; a solution for the
optimal material composition and adjustment schedule; and the incorporation of
these material adjustments into the nuclear burnup solution as determined by
SERPENT2.
\\
In the following sections the inner workings of ADER will be laid out and
explained. The functions will first be organized by themes of collective
action and then elaborated upon alphabetically. A special section, 
\ref{sec:serpent_funs}, will detail a handful of intrinsic SERPENT2 functions,
an understanding of which will facilitate such of ADER.
\\
In section \ref{sec:ader_input} the functions relating to the interpretation
of user input will be detailed. Section \ref{sec:ader_setup} will detail those
functions that sort and link user input into the necessary data structures.
Section \ref{sec:ader_opt} will detail those functions which construct and
solve the optimization problem. Section \ref{sec:ader_burn} will detail those
functions that handle the burnup solution. Section \ref{sec:ader_output} will
detail those functions which output data to the user. Section 
\ref{sec:ader_test} will detail those functions involved with the testing of
ADER. Section \ref{sec:ader_para} will detail some of the methodology
behind parallel computation with ADER.\\
As a final note it needs to be mentioned up front that SERPENT2 makes extensive
use of linked-lists and the term ``\texttt{ptr}". A ``\texttt{ptr}" in this
sense is not a C-style pointer, a variable which contains a memory address, but
the index of a monolithic array at which the desired data may be found. For
instance, if \texttt{NUMBER-OF-CAT-LEGS-PTR = 6} then one would 
expect that at \texttt{CAT-DATA-ARRAY[6]} would be the value ``\texttt{4}".
C-style pointers are referred to simply as pointers.\\

\section{Inside SERPENT2}\label{sec:serpent_funs}
\input{serpent_funs}

\section{ADER Input} \label{sec:ader_input}
\input{ader_input}

\section{ADER Setup} \label{sec:ader_setup}
\input{ader_setup}

\section{ADER Optimization} \label{sec:ader_opt}
\input{ader_opt}

\section{ADER Burnup} \label{sec:ader_burn}
\input{ader_burn}

\section{ADER Output} \label{sec:ader_output}
\input{ader_ouput}

\section{ADER Testing} \label{sec:ader_test}
\input{ader_test}

\section{ADER in Parallel} \label{sec:ader_para}
\input{ader_para}
\end{document}
