Considering that ADER is a source code modification to the SERPENT2 base a basic
understanding of SERPENT2 programming is essential for working in ADER. The
following is \textit{not} intended to be a SERPENT2 API nor will it have near
as much detail. Rather, this section is meant to introduce the reader to key
SERPENT2 structures so that the reader is then prepared to discover more
on their own.
The first aspect of SERPENT2 to grasp is not a function but an array - in fact
it is best of think of this array as an object from the priciples of
object-oriented programming. The \texttt{WDB}, or 
\textbf{W}rite \textbf{D}ata\textbf{B}ase, is a monolithic array of doubles.
\texttt{RDB} is a write-protected cast of \texttt{WDB}. \texttt{WDB} holds
almost all of the program information for SERPENT2 cast as a \texttt{double} and
formatted as an array of linked lists.
The header file, \texttt{locations.h}, holds the initial data structure that
\texttt{WDB} is built from - this is where the initial array location for
the first item in each linked list can be found.
Additionally, and of less importance, are the following arrays: \texttt{PRIVA}
is a doubles array for OpenMP data, \texttt{BUF} is a short term accumulation
array, \texttt{RES1} is a doubles array generally for holding results pulled
from \texttt{BUF}, \texttt{RES2} is an array used for memory optimization in the
burnup routines as is \texttt{RES3} while both are involved with the threaded
behavior of SERPENT2, \texttt{ASCII} is a \texttt{char*} array.
An important concept to keep in mind is that the location of data in all of
these arrays is described by the data in \texttt{WDB}. This data is accessed and
manipulated by functions inside of SERPENT2. While C is not an object-oriented
language by default SERPENT2 behaves as an object-oriented program in that
many of its objects, these data arrays, should only be acted on by specific
methods, functions inside of SEPRENT.  Before diving in to these
functions it should be noted that many variables in SERPENT2 have some name of
``\texttt{ptr}" or a varient thereof. These variables do not indicate C-style
pointers - variables declared with an ``\texttt{*}". Rather they are usually
an array index at which some data of interest can be found. This is mentioned
as the naming convention could cause confusion.

\subsection{AverageTransmuXS}
\input{funs/AverageTransmuXS}

\subsection{BurnMaterials}
\input{funs/BurnMaterials}

\subsection{BurnMatrixSixe}
\input{funs/BurnMatrixSize}

\subsection{BurnupCycle}
\input{funs/BurnupCycle}

\subsection{CalculateTransmuXS}
\input{funs/CalculateTransmuXS}

\subsection{GetPrivateData}
\input{funs/GetPrivateData}

\subsection{GetText}
\input{funs/GetText}

\subsection{MaterialBurnup}
\input{funs/MaterialBurnup}

\subsection{MakeBurnMatrix}
\input{funs/MakeBurnMatrix}

\subsection{NewItem}
\input{funs/NewItem}

\subsection{NextItem}
\input{funs/NextItem}

\subsection{PrepareTransportCycle}
\input{funs/PrepareTransportCycle}

\subsection{PrintDepOutput}
\input{funs/PrintDepOutput}

\subsection{ProcessMaterials}
\input{funs/ProcessMaterials}

\subsection{ReadInput}
\input{funs/ReadInput}

\subsection{StoreTransmuXS}
\input{funs/StoreTransmuXS}

\subsection{TestParam}
\input{funs/TestParam}

\subsection{TransportCycle}
\input{funs/TransportCycle}
